---
title: "Income analysis using Logistic Regression"
output: html_notebook
---

#### Setup
first load some library...

```{r}
library(ggplot2)
library(stats)
library(dplyr)
```

- It's time to read data...
```{r}
adult <- read.csv("adult.csv")
head(adult)
```


- Let's checkout the structure of the variables and their summary..
```{r}
str(adult)
```


```{r}
summary(adult)
```



### Data Cleaning

We have a lot of categorical variables, with too many factors that may be neccessary for model building. In this section, we'll collapse factors for
these columns into fewer categories.

#### Type Employer
Let's check out the frequency of the different factor levels in this column.

```{r}
table(adult$workclass)
```

We'll combine similar looking factor levels into single levels.
```{r}
levels(adult$workclass)[4] <- "Unemployed"
levels(adult$workclass)[9] <- "Unemployed"
levels(adult$workclass)[3] <- "SL-gov"
levels(adult$workclass)[8] <- "SL-gov"
levels(adult$workclass)[6:7] <- "self-emp"
```

Okay, Now re-check it...
```{r}
table(adult$workclass)
```


#### Marital Status
- We'll do the same for this column.
```{r}
levels(adult$marital.status)[1] <- "Not-Married"
levels(adult$marital.status)[6:7] <- "Not-Married"
levels(adult$marital.status)[2:4] <- "Married"

table(adult$marital.status)
```


#### Countries into region
Again, We have too many countries to deal with. It makes sense to convert them into regions. Let's build vectors for regions.

```{r}
Asia <-c('China','Hong','India','Iran','Cambodia','Japan', 'Laos' ,
          'Philippines' ,'Vietnam' ,'Taiwan', 'Thailand')
North.America <- c('Canada','United-States','Puerto-Rico' )

Europe <- c('England' ,'France', 'Germany' ,'Greece','Holand-Netherlands','Hungary',
            'Ireland','Italy','Poland','Portugal','Scotland','Yugoslavia')

Latin.and.South.America <- c('Columbia','Cuba','Dominican-Republic','Ecuador',
                             'El-Salvador','Guatemala','Haiti','Honduras',
                             'Mexico','Nicaragua','Outlying-US(Guam-USVI-etc)','Peru',
                            'Jamaica','Trinadad&Tobago')
Other <- c('South')
```

- Function to set county according to their continent...
```{r}
group_country <- function(ctry){
  if(ctry %in% Asia){
      return ('Asia')
  }else if(ctry %in% North.America){
    return('North.America')
  }else if(ctry %in% Europe){
    return('Europe')
  }else if(ctry %in% Latin.and.South.America){
    return('Latin.and.South.America')
  }else {
    return ('Other')
  }
}
```

- Now time to apply our above function...
```{r}
adult$native.country <- sapply(adult$native.country,group_country)
```
```{r}
colnames(adult)[14] <- "region"
table(adult$region)
```

### Missing Data

- Now it's time to deal with missing data...

```{r}
# Load library first
library(Amelia)
```



```{r}
adult[adult=="?"]<-NA
```

Refactoring the columns...
```{r}
adult$workclass <- factor(adult$workclass)
adult$region <- factor(adult$region)
adult$marital.status <- factor(adult$marital.status)
adult$occupation <- factor(adult$occupation)
```

- Creating a missing map for the data

```{r}
missmap(adult,y.at = c(1),y.labels = c(" "),col=c("yellow","black"))
```


- Ommiting missing vales...
```{r}
adult <- na.omit(adult)
```

- Now, check missing map again for conformation...
```{r}
missmap(adult,y.at = c(1),y.labels = c(" "),col=c("yellow","black"))
```


- Wow !!! Missing data is now gone....

### Exploratory Data Analysis

- Histogram of ages, by income...

```{r}
ggplot(adult,aes(age)) + geom_histogram(aes(fill=income),color='black',binwidth = 1)+theme_bw()
```


- Histogram of hours worked per week...

```{r}
ggplot(adult,aes(hours.per.week))+geom_histogram()+theme_bw()
```



- Barplot of region filled by income class...
```{r}
ggplot(adult,aes(region))+geom_bar(aes(fill=income),color="black")+theme_bw()+theme(axis.text.x = element_text(angle = 45,hjust=1))
```



### Model Building

- Now, we'll build a model to classify people into two groups: above or below 50k in salary. It makes sense to use logistic regression here as we're
  trying to predict binary outcome.
  
- Splitting data for training set

```{r}
library(caTools)

# Splitting the data into 70% training and 30% test
sample <- sample.split(adult$income,SplitRatio = 0.7)
train <- subset(adult,sample==TRUE)
test <- subset(adult,sample==FALSE)
```

- check data in test and train

```{r}
head(test)
```

```{r}
head(train)
```


- Creating the model...

```{r}
model <- glm(income ~ .,family = binomial(logit),data=train)
```

```{r}
summary(model)
```

- Removing unimportant features iteratively using 'step'...
```{r}
new.step.model <- step(model)
```


- Predictions and Checking results, we'll use the new step model for this...

```{r}
test$predicted.income <- predict(new.step.model,newdata=test,type="response")
table(test$income,test$predicted.income>0.5)
```

