---
title: "R Notebook"
output: html_notebook
---
Before we go into game of data, we need to install some library. If you have already installed , You can ignore

```{r eval=FALSE}
install.packages("ggplot2")
install.packages("readr")
install.packages("gridExtra")
install.packages("grid")
install.packages("plyr")
```

Once you have installed all above packages, Now we need to import all packages in our project
```{r}
library(ggplot2)
library(readr)
library(gridExtra)
library(grid)
library(plyr)
```

Now, our library are alredy loaded so not let's play with data...

# Load Data
```{r}
iris=read.csv('/home/kunal/Documents/DS/Iris/iris/Iris.csv')
```

# Have Look to our data
```{r}
data(iris)
iris[sample(nrow(iris),10),]
```

```{r}
summary(iris)
```

# Visualization
Best way To analyse...

#### Sepal Length(Frequency Analysis)
```{r}
HisSl <- ggplot(data=iris,aes(x=SepalLengthCm))+
  geom_histogram(binwidth = 0.2,color="black",aes(fill=Species))+
  xlab("Sepal Lenght (cm)") +
  ylab("Frequency")+
  theme(legend.position ="none")+
  ggtitle("Histogram of Sepal Length")+
  geom_vline(data=iris,aes(xintercept= mean(SepalLengthCm)),linetype="dashed",color="red")+
  geom_vline(data=iris,aes(xintercept= median(SepalLengthCm)),linetype="dashed",color="blue")
          
```
```{r}
HisSl
```


#### Sepal Width(Frequency Analysis)
```{r}
HistSw <- ggplot(data=iris,aes(x=SepalWidthCm)) +
  geom_histogram(binwidth = 0.2,color="black",aes(fill=Species)) +
  
  xlab("Sepal Width (cm)") +
  ylab("Frequency") +
  theme(legend.position = "none") +
  ggtitle("Histogram of Sepal Width") +
  geom_vline(data=iris,aes(xintercept=mean(SepalWidthCm)),linetype="dashed",color="grey")

```

```{r}
HistSw
```


#### Petal Length(Frequency Analysis)
```{r}
HistPl <- ggplot(data=iris,aes(x=PetalLengthCm)) +
  geom_histogram(binwidth = 0.2,color="black",aes(fill=Species)) +
  xlab("Petal Length (cm)") +
  ylab("Frequency") +
  theme(legend.position = "none") +
  ggtitle("Histogram of Petal Length") +
  geom_vline(data=iris,aes(xintercept=mean(PetalLengthCm)),linetype="dashed",color="grey")

```

```{r}
HistPl
```


#### Petal Width(Frequency Analysis)
```{r}
HistPw <- ggplot(data=iris,aes(PetalWidthCm)) +
  geom_histogram(binwidth = 0.2,color="black",aes(fill=Species)) +
  xlab("Petal Width (cm)") +
  ylab("Frequency") +
  theme(legend.position = "none") +
  ggtitle("Histogram of Petal Width") +
  geom_vline(data=iris,aes(xintercept=mean(PetalWidthCm)),linetype="dashed",color="grey")

```

```{r}
HistPw
```

#### Now time to have look at the picture of Data
Just a Simple Plot of Data
```{r}
plot(iris)
```
For Histogram Fan
```{r}
grid.arrange(HisSl+ggtitle(""),
             HistSw+ggtitle(""),
             HistPl+ggtitle(""),
             HistPw+ggtitle(""),
             nrow=2,
             top=textGrob("Iris Frequency Histogram Table",gp=gpar(fontsize=15)))                                                              
```







